Working Draft: Lack of Unified Approaches Angle

### 2023-06-02 working-drafts/angle2.tex
Add early working draft outlines.

\title{Working Draft: Formalization Gap Angle}

@@

\section{Introduction}
\begin{itemize}
\item The PL community has embraced mechanization in the last decade
  \begin{itemize}
  \item POPLMark helped get the community on track for more mechanizations
  \item Since POPLMark, the number of formal proofs accompanying papers at POPL and PLDI has grown
  \end{itemize}
\item The concurrency community has not embraced mechanization
  \begin{itemize}
  \item The number of formal proofs accompanying papers at CONCUR is low and has not followed the trend at POPL/PLDI
  \end{itemize}
\item We propose a new benchmark for the specific issues present in concurrency
  \begin{itemize}
  \item A goal is to help develop momentum for more mechanizations
  \item A goal is to help develop a culture of mechanization
  \item A goal is to rally the community for collaborating on mechanizations
  \end{itemize}
\item Benchmarks cannot address every technique and field at once
  \begin{itemize}
  \item Challenges have to be simple enough to be manageable
  \item Challenges should not be encumbered by too many technical details
  \end{itemize}
\item POPLMark Reloaded extends the scope to proofs using logical relations
  \begin{itemize}
  \item Logical relations are crucial in many current developments
  \end{itemize}
\item Our benchmark extends the scope to process calculi and behavioural types
\item There are three key aspects that cause issues when mechanizing process calculi and behavioural types
  \begin{itemize}
  \item Scope extrusion in name passing systems generalises binders that makes techniques from lambda calculi inconvenient
  \item Linearity in behavioural type systems causes problems since linearity is generally not well supported
  \item Infinite behaviour modelled with coinduction causes problems since coinduction is generally not well supported
  \end{itemize}
\item Each part of our benchmark exercises the three aspects independently
  \begin{itemize}
  \item Real research projects will often need more than just one aspect
  \item We exercise each in isolation to keep solutions small
  \item We do not address how to combine techniques for the three aspects
  \end{itemize}
\item The problems we propose have been mechanized before
  \begin{itemize}
  \item A goal is to enable comparison between solutions using different techniques
  \item Our challenges are simple settings where we can compare techniques without distractions
  \end{itemize}
\end{itemize}

>>>>

\title{Working Draft: Lack of Unified Approaches Angle}

@@

\section{Introduction}
\begin{itemize}
\item The PL community has embraced mechanization in the last decade
  \begin{itemize}
  \item POPLMark helped get the community on track for more mechanizations
  \item Since POPLMark, the number of formal proofs accompanying papers has grown
  \end{itemize}
\item The concurrency community has not embraced mechanization to the same extent
\item We propose a new benchmark for the specific issues present in concurrency
  \begin{itemize}
  \item A goal is to help develop momentum for more mechanizations
  \item A goal is to help develop a culture of mechanization
  \item A goal is to rally the community for collaborating on mechanizations
  \end{itemize}
\item Benchmarks cannot address every technique and field at once
  \begin{itemize}
  \item Challenges have to be simple enough to be manageable
  \item Challenges should not be encumbered by too many technical details
  \end{itemize}
\item POPLMark Reloaded extends the scope to proofs using logical relations
  \begin{itemize}
  \item Logical relations are crucial in many current developments
  \end{itemize}
\item Our benchmark extends the scope to process calculi and behavioural types
\item There are three key aspects that cause issues when mechanizing process calculi and behavioural types
  \begin{itemize}
  \item Scope extrusion in name passing systems generalises binders that makes techniques from lambda calculi inconvenient
  \item Linearity in behavioural type systems causes problems since linearity is generally not well supported
  \item Infinite behaviour modelled with coinduction causes problems since coinduction is generally not well supported
  \end{itemize}
\item Each part of our benchmark exercises the three aspects independently
  \begin{itemize}
  \item Real research projects will often need more than just one aspect
  \item We exercise each in isolation to keep solutions small
  \item We do not address how to combine techniques for the three aspects
  \end{itemize}
\item The problems we propose have been mechanized before
  \begin{itemize}
  \item A goal is to enable comparison between solutions using different techniques
  \item Our challenges are simple settings where we can compare techniques without distractions
  \end{itemize}
\end{itemize}
